Summary Tables

### 2020-02-21 summary_tables.Rmd
Add true dist, and also add TOC

---
title: "Summary Tables"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

@@

>>>>

---
title: "Summary Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    theme: united
---

@@

## True Distance by total population
### Tables

  df <- io[[city]]$true_dist
  print(kable(df, caption = paste("True distance by mode for  ", city)))
}
